\ttitle

### 2015-06-04 Chapters/Introduction.tex
More updates to introduction

\subsection{Jaundice and postoperative outcomes}
\subsection{Role of preoperative biliary drainage}
%fang_pre-operative_2012 - Cochrane review
%wang_preoperative_2008 - Cochrane review

>>>>

\subsection{Role of preoperative biliary drainage and outcome after pancreaticoduodenectomy}
The increased incidence of adverse events after surgery in patients with obstructive jaundice resulted in routine preoperative biliary drainage becoming the standard practice in patients undergoing major pancreatic surgery. However, several studies over the past 20 years have challenged this paradigm. There appears to be increasing evidence that preoperative biliary drainage may be associated with increased morbidity both as a consequence of the drainage procedure itself as well as from infectious complications after surgery.

The paucity of good quality evidence on the role of preoperative biliary drainage in patients with obstructive jaundice undergoing major surgery and the lack of clear guidelines on the perioperative management of the jaundiced patients has resulted in wide variation in practice across different centres.

The effect of obstructive jaundice on cardiopulmonary exercise testing in patients with pancreatic disease has not been reported previously. Chapter \ref{ch_cpet_jaundice} reports on the investigation into the relationship between obstructive jaundice and preoperative cardiopulmonary exercise testing.

\subsection{Role of preoperative biliary drainage}
%fang_pre-operative_2012 - Cochrane review
%wang_preoperative_2008 - Cochrane review
